---
title: "Paper JAE"
author: "Jerico Fiestas Flores"
date: "2026-04-25"
output: html_document
---

## Loading packages and data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(haven)
library(table1)
library(dplyr)
library(gtsummary)
library(openxlsx)
library(WebPower)
library(effsize)
library(vcd)
library(BayesFactor)
library(ggplot2)
library(car)
library(tidyr)


data = read_dta("total_session_data.dta")
data = data[data$session>0,] ## Eliminate pilot session

data <- mutate(data,
  female = ifelse(sex==2,1,0),
  employed = ifelse (work<3,1,0), 
  volunteer = ifelse(volunteer==2,0,1),
  treatment = as.factor(treatment),
  bid = as.factor(bid),
  hypo = ifelse(treatment==3,1,0),
  conq = ifelse(treatment==2,1,0)
  )


table(data$work)

```


## Table 2: Data description Demographics

```{r}

# Create render function for table
my_render <- function(x, ...) {
  x <- as.numeric(x)
  n <- sum(!is.na(x))
  if (n == 0) return("")
  m <- mean(x, na.rm = TRUE)
  se <- sd(x, na.rm = TRUE) / sqrt(n)
  sprintf("%.4f<br>(%.4f)", m, se)  
}


# Create the Table 1
# Column 1
t1_c1 = table1(~ female + year + employed + volunteer + eco_fin, 
       data = data, 
       render = my_render,
       extra.cols = NULL) 

# Column 2-7
t1_c2_7 = table1(~ female + year + employed + volunteer + eco_fin | bid+ treatment, 
       data = data, 
       render = my_render,
       extra.cols = NULL) 

print(t1_c1)
print(t1_c2_7)


```





## Table 3: Vote Results

```{r}

results = table1(~ i_vote| bid+ treatment, 
       data = data, 
       render = my_render,
       extra.cols = NULL)

## PENDING: USE THE RESULTS FROM RESULTS TABLE FOR THE VALUES TO BE USED IN THE FOLLOWING FUNCTIONS

## Study N range
alpha_test <- 0.05 / 3 #Bonferroni test
wp.t(n1 = NULL, d = 0.5, power = 0.8, type = "two.sample", alpha = alpha_test) # n= 85
wp.t(n1 = NULL, d = 0.45, power = 0.8, type = "two.sample", alpha = alpha_test) # n=104
wp.t(n1 = NULL, d = 0.34, power = 0.8, type = "two.sample", alpha = alpha_test) # n=182
d_p = 0.35
d_p2 = 0.5


## Study power
r = 115 # Real sample
c = 109 # Consequential sample
h = 119 # Hypothetical sample

# For hyphotetical against real pooled
wp.t(n1=r, n2=h, d=d_p, power=NULL, type='two.sample.2n') #Study power
wp.t(n1=c, n2=h, d=d_p, power=NULL, type='two.sample.2n') #Study power

wp.t(n1=r, n2=h, d=d_p2, power=NULL, type='two.sample.2n') #Study power
wp.t(n1=c, n2=h, d=d_p2, power=NULL, type='two.sample.2n') #Study power

# For hyphotetical against bid 3

r1 = 61 # Real sample
c1 = 52 # Consequential sample
h1 = 60 # Hypothetical sample

wp.t(n1=r1, n2=h1, d=d_p, power=NULL, type='two.sample.2n') #Study power
wp.t(n1=c1, n2=h1, d=d_p, power=NULL, type='two.sample.2n') #Study power

wp.t(n1=r1, n2=h1, d=d_p2, power=NULL, type='two.sample.2n') #Study power
wp.t(n1=c1, n2=h1, d=d_p2, power=NULL, type='two.sample.2n') #Study power

# For hyphotetical against bid 8
r2 = 54 # Real sample
c2 = 57 # Consequential sample
h2 = 59 # Hypothetical sample

wp.t(n1=r2, n2=h2, d=d_p, power=NULL, type='two.sample.2n') #Study power
wp.t(n1=c2, n2=h2, d=d_p, power=NULL, type='two.sample.2n') #Study power

wp.t(n1=r2, n2=h2, d=d_p2, power=NULL, type='two.sample.2n') #Study power
wp.t(n1=c2, n2=h2, d=d_p2, power=NULL, type='two.sample.2n') #Study power


#####################################
## Effect size
#####################################
## Pooled

R_vs_H <- subset(data, treatment %in% c(1, 3))
R_vs_H$treatment <- droplevels(R_vs_H$treatment)
cohen.d(i_vote ~ treatment, data = R_vs_H)

R_vs_C <- subset(data, treatment %in% c(2, 3))
R_vs_C$treatment <- droplevels(R_vs_C$treatment)
cohen.d(i_vote ~ treatment, data = R_vs_C)

## 3

R_vs_H_3 <- subset(data, treatment %in% c(1, 3)& bid == 3)
R_vs_H_3$treatment <- droplevels(R_vs_H_3$treatment)
cohen.d(i_vote ~ treatment, data = R_vs_H_3)

R_vs_C_3 <- subset(data, treatment %in% c(2, 3)& bid == 3)
R_vs_C_3$treatment <- droplevels(R_vs_C_3$treatment)
cohen.d(i_vote ~ treatment, data = R_vs_C_3)


## 8

R_vs_H_8 <- subset(data, treatment %in% c(1, 3)& bid == 8)
R_vs_H_8$treatment <- droplevels(R_vs_H_8$treatment)
cohen.d(i_vote ~ treatment, data = R_vs_H_8)

R_vs_C_8 <- subset(data, treatment %in% c(2, 3)& bid == 8)
R_vs_C_8$treatment <- droplevels(R_vs_C_8$treatment)
cohen.d(i_vote ~ treatment, data = R_vs_C_8)


######################
## Chi2 test and Cramer V
#####################

## Pooled
ct <- table(data$treatment, data$i_vote)
ct
chisq_result <- chisq.test(ct, correct = FALSE) 
chisq_result
assoc <- assocstats(ct)
assoc$cramer   # Cramér's V

## 3
data3 <- subset(data, bid==3)
ct3 <- table(data3$treatment, data3$i_vote)
ct3
chisq_result <- chisq.test(ct3, correct = FALSE)  
chisq_result
assoc <- assocstats(ct3)
assoc$cramer   # Cramér's V


## 8
data8 <- subset(data, bid==8)
ct8 <- table(data8$treatment, data8$i_vote)
ct8
chisq_result <- chisq.test(ct8, correct = FALSE)  
chisq_result
assoc <- assocstats(ct8)
assoc$cramer   # Cramér's V


#####################################
## Sample power (Actual power)
#####################################

# Pooled
dr1=(0.8348-0.7815)/0.5
dr2=(0.7982-0.7815)/0.5

wp.t(n1=r, n2=h, d=dr1, power=NULL, type='two.sample.2n') #current
wp.t(n1=c, n2=h, d=dr2, power=NULL, type='two.sample.2n') #current

# For bid 3

# For hyphotetical against bid 3

dr1=(0.7541-0.70)/0.5
dr2=(0.6538-0.70)/0.5

wp.t(n1=r1, n2=h1, d=dr1, power=NULL, type='two.sample.2n') #current
wp.t(n1=c1, n2=h1, d=dr2, power=NULL, type='two.sample.2n') #current

#For bid 8

dr1=(0.9259-0.8644)/0.5
dr2=(0.9298-0.8644)/0.5

wp.t(n1=r2, n2=h2, d=dr1, power=NULL, type='two.sample.2n') #current
wp.t(n1=c2, n2=h2, d=dr2, power=NULL, type='two.sample.2n') #current


```

## Table 4: Compensation effect

```{r}
model_1 <- model_1 <- glm(i_vote ~ bid + day_time, 
               data = data, 
               family = binomial(link = "logit"))
summary(model_1)
AIC(model_1)
BIC(model_1)
log_lik <- as.numeric(logLik(model_1))


model_2 <- glm(i_vote ~ bid+day_time+ female+year+employed+eco_fin+volunteer, data = data, family = "binomial")
summary(model_2)
AIC(model_2)
BIC(model_2)
logLik(model_2)


model_3 <- glm(i_vote ~ bid+day_time+ female+year+employed+eco_fin+volunteer+busy+useful, data = data, family = "binomial")
summary(model_3)
AIC(model_3)
BIC(model_3)
logLik(model_3)



```

## Table 5: Treatment effect



## Table 6: Average certainty level by compensation and treatment

```{r}

# Create render function for table
my_render <- function(x, ...) {
  x <- as.numeric(x)
  n <- sum(!is.na(x))
  if (n == 0) return("")
  m <- mean(x, na.rm = TRUE)
  se <- sd(x, na.rm = TRUE) / sqrt(n)
  sprintf("%.3f<br>(%.4f)", m, se)  
}


table1(~ cert | bid, 
       data = data, 
       render = my_render,
       extra.cols = TRUE) 


tcert = table1(~ cert | bid+ treatment, 
       data = data, 
       render = my_render,
       extra.cols = TRUE) 

print(tcert)


### Pairwise inside each group
  pairwise_result <- pairwise.t.test(
    x = data$cert,
    g = data$treatment,
    p.adjust.method = "bonferroni",
    pool.sd = FALSE  ) # Welch approximation


# Function to perform pairwise t‑tests with Bonferroni for a given bid
compare_within_bid <- function(data, bid_value) {
  subset_data <- subset(data, bid == bid_value)
  # Pairwise t‑tests (Welch approximation, no pooling)
  pairwise_result <- pairwise.t.test(
    x = subset_data$cert,
    g = subset_data$treatment,
    p.adjust.method = "bonferroni",
    pool.sd = FALSE   # Welch approximation
  )
  print(paste("Bid =", bid_value))
  print(pairwise_result)
}

# Run for bid = 3 and bid = 8
compare_within_bid(data, 3)
compare_within_bid(data, 8)


# For each treatment, compare between groups
treatments <- c(1, 2, 3)

for (tr in treatments) {
  cert_bid3 <- data$cert[data$treatment == tr & data$bid == 3]
  cert_bid8 <- data$cert[data$treatment == tr & data$bid == 8]
  
  test_result <- t.test(cert_bid3, cert_bid8, var.equal = FALSE)  # Welch
  cat("\nTreatment", tr, "\n")
  print(test_result)
}

for (tr in treatments) {
  cert_bid3 <- data$cert[data$treatment == tr & data$bid == 3]
  cert_bid <- data$cert[data$treatment == tr ]
  
  test_result <- t.test(cert_bid3, cert_bid, var.equal = FALSE)  # Welch
  cat("\nTreatment", tr, "\n")
  print(test_result)
}

for (tr in treatments) {
  cert_bid8 <- data$cert[data$treatment == tr & data$bid == 8]
  cert_bid <- data$cert[data$treatment == tr ]
  
  test_result <- t.test(cert_bid8, cert_bid, var.equal = FALSE)  # Welch
  cat("\nTreatment", tr, "\n")
  print(test_result)
}


```


## Graph 2: Certainty levels

```{r}

# Compute mean and standard error per treatment × bid
summary_certt <- data %>%
  group_by(treatment) %>%
  summarise(
    mean_cert = mean(cert, na.rm = TRUE),
    se_cert = sd(cert, na.rm = TRUE) / sqrt(n()),
    var_cert = var(cert, na.rm = TRUE),   # add variance
    .groups = "drop"
  )

summary_cert <- data %>%
  group_by(treatment, bid) %>%
  summarise(
    mean_cert = mean(cert, na.rm = TRUE),
    se_cert = sd(cert, na.rm = TRUE) / sqrt(n()),
    var_cert = var(cert, na.rm = TRUE),   # add variance
    .groups = "drop"
  )

# Convert treatment and bid to factors for better labels
data_g = data
data_g$treatment <- factor(data_g$treatment, levels = c(1,2,3), 
                         labels = c("Real", "Consequential", "Hypothetical"))
data_g$bid <- factor(data_g$bid, levels = c(3,8), labels = c("$3", "$8"))

# Compute mean certainty per treatment and bid
mean_data <- data_g %>%
  group_by(treatment, bid) %>%
  summarise(mean_cert = mean(cert, na.rm = TRUE), .groups = "drop")

# Plot with custom colors and no vertical grids
ggplot(data_g, aes(x = cert, color = bid, fill = bid)) +
  geom_density(alpha = 0.3) +
  geom_vline(data = mean_data, aes(xintercept = mean_cert, color = bid),
             linetype = "dashed", linewidth = 0.8) +
  facet_wrap(~ treatment, ncol = 3) +
  labs(x = "Certainty", y = "Density", color = "Bid", fill = "Bid") +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "right",
    panel.grid.major.x = element_blank(),   # remove major vertical grid lines
    panel.grid.minor.x = element_blank()    # remove minor vertical grid lines
  ) +
  # Choose your color palette (example: custom colors for $3 and $8)
  scale_color_manual(values = c("$3" = "#E69F00", "$8" = "#56B4E9")) +
  scale_fill_manual(values = c("$3" = "#E69F00", "$8" = "#56B4E9"))

# Save the plot
ggsave("density_treatment_bid_with_means.png", width = 10, height = 4, dpi = 300)


## Group variance test

# Ensure treatment and bid are factors
data$treatment <- factor(data$treatment)
data$bid <- factor(data$bid)

# Create a combined group variable
data$group <- interaction(data$treatment, data$bid)

# Levene's test (median-based, robust)
leveneTest(cert ~ group, data = data, center = median)

# For bid = 3
data_bid3 <- subset(data, bid == 3)

# Pairwise F-tests
pairwise_var <- function(var1, var2) {
  var.test(var1, var2)$p.value
}

treatments <- c(1,2,3)
p_vals <- c()
k <- 1
for (i in 1:2) {
  for (j in (i+1):3) {
    group1 <- data_bid3$cert[data_bid3$treatment == i]
    group2 <- data_bid3$cert[data_bid3$treatment == j]
    p_vals[k] <- var.test(group1, group2)$p.value
    k <- k+1
  }
}
p_adj <- p.adjust(p_vals, method = "bonferroni")
p_adj

# For bid = 8
data_bid8 <- subset(data, bid == 8)

# Pairwise F-tests
pairwise_var <- function(var1, var2) {
  var.test(var1, var2)$p.value
}

treatments <- c(1,2,3)
p_vals <- c()
k <- 1
for (i in 1:2) {
  for (j in (i+1):3) {
    group1 <- data_bid8$cert[data_bid8$treatment == i]
    group2 <- data_bid8$cert[data_bid8$treatment == j]
    p_vals[k] <- var.test(group1, group2)$p.value
    k <- k+1
  }
}
p_adj <- p.adjust(p_vals, method = "bonferroni")
p_adj

## For all
treatments <- c(1,2,3)
p_vals <- c()
k <- 1
for (i in 1:2) {
  for (j in (i+1):3) {
    group1 <- data$cert[data$treatment == i]
    group2 <- data$cert[data$treatment == j]
    p_vals[k] <- var.test(group1, group2)$p.value
    k <- k+1
  }
}
p_adj <- p.adjust(p_vals, method = "bonferroni")
p_adj



#####################################
## Effect size
#####################################
## Pooled

R_vs_H <- subset(data, treatment %in% c(1, 3))
R_vs_H$treatment <- droplevels(R_vs_H$treatment)
cohen.d(cert ~ treatment, data = R_vs_H)

R_vs_C <- subset(data, treatment %in% c(2, 3))
R_vs_C$treatment <- droplevels(R_vs_C$treatment)
cohen.d(cert ~ treatment, data = R_vs_C)

## 3

R_vs_H_3 <- subset(data, treatment %in% c(1, 3)& bid == 3)
R_vs_H_3$treatment <- droplevels(R_vs_H_3$treatment)
cohen.d(cert ~ treatment, data = R_vs_H_3)

R_vs_C_3 <- subset(data, treatment %in% c(2, 3)& bid == 3)
R_vs_C_3$treatment <- droplevels(R_vs_C_3$treatment)
cohen.d(cert ~ treatment, data = R_vs_C_3)

## 8

R_vs_H_8 <- subset(data, treatment %in% c(1, 3)& bid == 8)
R_vs_H_8$treatment <- droplevels(R_vs_H_8$treatment)
cohen.d(cert ~ treatment, data = R_vs_H_8)

R_vs_C_8 <- subset(data, treatment %in% c(2, 3)& bid == 8)
R_vs_C_8$treatment <- droplevels(R_vs_C_8$treatment)
cohen.d(cert ~ treatment, data = R_vs_C_8)

```


## Table 7: Transformations due certaintiy

```{r}

# Convert treatment to labelled factor (optional)
data <- data %>%
  mutate(treatment = factor(treatment, levels = c(1,2,3),
                            labels = c("Real", "Consequential", "Hypothetical")))
data8 <- subset(data, bid==8)
data3 <- subset(data, bid==3) # Change depending the desired bid grup

# Function to apply recoding rules
# rule: "eq2" = recode against (0) to in favor (1) when cert <= Ci
#       "eq3" = recode in favor (1) to against (0) when cert <= Ci
recode_vote <- function(vote, cert, Ci, rule) {
  if (rule == "eq2") {
    # If vote == 0 (against) and certainty <= Ci, change to 1 (in favor)
    ifelse(vote == 0 & cert <= Ci, 1, vote)
  } else if (rule == "eq3") {
    # If vote == 1 (in favor) and certainty <= Ci, change to 0 (against)
    ifelse(vote == 1 & cert <= Ci, 0, vote)
  } else {
    vote
  }
}

# Thresholds to test
ci_thresholds <- c(5, 6, 7, 8)

# Helper function to compute percentages for one rule and one threshold
get_percent <- function(data, rule, Ci) {
  data %>%
    mutate(vote_corrected = recode_vote(i_vote, cert, Ci, rule)) %>%
    group_by(treatment) %>%
    summarise(
      prop = mean(vote_corrected, na.rm = TRUE) * 100,
      .groups = "drop"
    )
}

# Original percentages (no correction)
orig_perc <- data8 %>%
  group_by(treatment) %>%
  summarise(orig = mean(i_vote, na.rm = TRUE) * 100, .groups = "drop")
orig_perc

# Compute percentages for Eq.2 (recoding against -> in favor)
eq2_results <- lapply(ci_thresholds, function(Ci) {
  get_percent(data8, "eq2", Ci) %>%
    rename(!!paste0("Ci<=", Ci) := prop)
}) %>% bind_cols()
eq2_results

# Compute percentages for Eq.3 (recoding in favor -> against)
eq3_results <- lapply(ci_thresholds, function(Ci) {
  get_percent(data8, "eq3", Ci) %>%
    rename(!!paste0("Ci<=", Ci) := prop)
}) %>% bind_cols() 
eq3_results



```

## Table 8: Change vote regression


```{r}

model_1 <- glm(ch_vote ~cert, 
               data = data, 
               family = binomial(link = "logit"))
summary(model_1)
AIC(model_1)
BIC(model_1)
logLik(model_1)
nobs(model_1)


model_2 <- glm(ch_vote ~cert+female+year+employed+eco_fin+volunteer, 
               data = data, 
               family = binomial(link = "logit"))
summary(model_2)
AIC(model_2)
BIC(model_2)
logLik(model_2)
nobs(model_2)

model_4 <- glm(ch_vote ~cert, 
               data = data8, 
               family = binomial(link = "logit"))
summary(model_4)
AIC(model_4)
BIC(model_4)
logLik(model_4)
nobs(model_4)


model_3 <- glm(ch_vote ~cert+female+year+employed+eco_fin+volunteer, 
               data = data8, 
               family = binomial(link = "logit"))
summary(model_3)
AIC(model_3)
BIC(model_3)
logLik(model_3)
nobs(model_3)

model_5 <- glm(ch_vote ~cert, 
               data = data3, 
               family = binomial(link = "logit"))
summary(model_5)
AIC(model_5)
BIC(model_5)
logLik(model_5)
nobs(model_5)


model_6 <- glm(ch_vote ~cert+female+year+employed+eco_fin+volunteer, 
               data = data3, 
               family = binomial(link = "logit"))
summary(model_6)
AIC(model_6)
BIC(model_6)
logLik(model_6)
nobs(model_6)



```


## SUPPLEMENTARY TABLES
## Table B1: Power analysis Lloyd-Smith and Adamowicz (2018) 

```{r}

## Sample power
# Power in (Lloyd-Smith and Adamowicz (2018)) Real - Hypothetical
d1=(0.694-0.468)/0.5 # Effect found in previous paper (Lloyd-Smith and Adamowicz (2018))
wp.t(n1=79, n2=62, d=d1, power=NULL, type='two.sample.2n') # Power in paper

# Power in (Lloyd-Smith and Adamowicz (2018)) Consequential - Hypothetical
d2=(0.639-0.468)/0.5 # Effect found in previous paper (Lloyd-Smith and Adamowicz (2018))
wp.t(n1=79, n2=61, d=d2, power=NULL, type='two.sample.2n') # Power in paper


data_matrix_2018 <- matrix(c(43, 19,   # Real: In Favor, Against total: 62 participants
                         39, 22,   # Consequential: In Favor, Against total: 61 participants
                         37, 42),  # Hypothetical: In Favor, Against total: 79 participants
                       nrow = 3,   # Number of rows (scenarios)
                       byrow = TRUE) # Fill the matrix by row
contingency_table_2018 <- as.table(data_matrix_2018)
chi_square_result_2018 <- chisq.test(contingency_table_2018, correct = FALSE) # correct=FALSE for no Yates' correction
V = sqrt( chi_square_result_2018$statistic / (202* (2 - 1)) )


```

## Table B3: Complementary 1: Equivalence testing
```{r}


# Real vs H test pooled
R_vs_H <- subset(data, treatment %in% c(1, 3))

# TOST independent samples t-test
# low_eqbound_d = -0.2, high_eqbound_d = 0.2 (negligible range)
TOSTtwo(
  m1 = mean(R_vs_H$i_vote[R_vs_H$treatment == 1]),
  m2 = mean(R_vs_H$i_vote[R_vs_H$treatment == 3]),
  sd1 = sd(R_vs_H$i_vote[R_vs_H$treatment == 1]),
  sd2 = sd(R_vs_H$i_vote[R_vs_H$treatment == 3]),
  n1 = sum(R_vs_H$treatment == 1),
  n2 = sum(R_vs_H$treatment == 3),
  low_eqbound_d = -0.3,
  high_eqbound_d = 0.3,
  alpha = 0.05
)


# Real vs C test pooled
R_vs_C <- subset(data, treatment %in% c(2, 3))

# TOST independent samples t-test
# low_eqbound_d = -0.2, high_eqbound_d = 0.2 (negligible range)
TOSTtwo(
  m1 = mean(R_vs_C$i_vote[R_vs_C$treatment == 2]),
  m2 = mean(R_vs_C$i_vote[R_vs_C$treatment == 3]),
  sd1 = sd(R_vs_C$i_vote[R_vs_C$treatment == 2]),
  sd2 = sd(R_vs_C$i_vote[R_vs_C$treatment == 3]),
  n1 = sum(R_vs_C$treatment == 2),
  n2 = sum(R_vs_C$treatment == 3),
  low_eqbound_d = -0.3,
  high_eqbound_d = 0.3,
  alpha = 0.05
)




# Real v H 3
R_vs_H_3 <- subset(data, treatment %in% c(1, 3) & bid == 3)

# TOST independent samples t-test
# low_eqbound_d = -0.2, high_eqbound_d = 0.2 (negligible range)
# alpha = 0.05 (or adjust for multiple comparisons)
TOSTtwo(
  m1 = mean(R_vs_H_3$i_vote[R_vs_H_3$treatment == 1]),
  m2 = mean(R_vs_H_3$i_vote[R_vs_H_3$treatment == 3]),
  sd1 = sd(R_vs_H_3$i_vote[R_vs_H_3$treatment == 1]),
  sd2 = sd(R_vs_H_3$i_vote[R_vs_H_3$treatment == 3]),
  n1 = sum(R_vs_H_3$treatment == 1),
  n2 = sum(R_vs_H_3$treatment == 3),
  low_eqbound_d = -0.3,
  high_eqbound_d = 0.3,
  alpha = 0.05
)

# Real v C 3
R_vs_C_3 <- subset(data, treatment %in% c(2, 3) & bid == 3)

# TOST independent samples t-test
TOSTtwo(
  m1 = mean(R_vs_C_3$i_vote[R_vs_C_3$treatment == 2]),
  m2 = mean(R_vs_C_3$i_vote[R_vs_C_3$treatment == 3]),
  sd1 = sd(R_vs_C_3$i_vote[R_vs_C_3$treatment == 2]),
  sd2 = sd(R_vs_C_3$i_vote[R_vs_C_3$treatment == 3]),
  n1 = sum(R_vs_C_3$treatment == 2),
  n2 = sum(R_vs_C_3$treatment == 3),
  low_eqbound_d = -0.3,
  high_eqbound_d = 0.3,
  alpha = 0.05
)


# Real vs H bid 8
R_vs_H_8 <- subset(data, treatment %in% c(1, 3) & bid == 8)

# TOST independent samples t-test
# low_eqbound_d = -0.2, high_eqbound_d = 0.2 (negligible range)
# alpha = 0.05 (or adjust for multiple comparisons)
TOSTtwo(
  m1 = mean(R_vs_H_8$i_vote[R_vs_H_8$treatment == 1]),
  m2 = mean(R_vs_H_8$i_vote[R_vs_H_8$treatment == 3]),
  sd1 = sd(R_vs_H_8$i_vote[R_vs_H_8$treatment == 1]),
  sd2 = sd(R_vs_H_8$i_vote[R_vs_H_8$treatment == 3]),
  n1 = sum(R_vs_H_8$treatment == 1),
  n2 = sum(R_vs_H_8$treatment == 3),
  low_eqbound_d = -0.3,
  high_eqbound_d = 0.3,
  alpha = 0.05
)

# Real vs C bid 8
R_vs_C_8 <- subset(data, treatment %in% c(2, 3) & bid == 8)

# TOST independent samples t-test
TOSTtwo(
  m1 = mean(R_vs_C_8$i_vote[R_vs_C_8$treatment == 2]),
  m2 = mean(R_vs_C_8$i_vote[R_vs_C_8$treatment == 3]),
  sd1 = sd(R_vs_C_8$i_vote[R_vs_C_8$treatment == 2]),
  sd2 = sd(R_vs_C_8$i_vote[R_vs_C_8$treatment == 3]),
  n1 = sum(R_vs_C_8$treatment == 2),
  n2 = sum(R_vs_C_8$treatment == 3),
  low_eqbound_d = -0.3,
  high_eqbound_d = 0.3,
  alpha = 0.05
)

```



## Table B4: Complementary 1: Bayesian
```{r}

R_vs_H <- subset(data, treatment %in% c(1, 3))
R_vs_H$treatment <- droplevels(R_vs_H$treatment)

bf_interval <- ttestBF(
  formula = i_vote ~ treatment,
  data = R_vs_H,
  nullInterval = c(-0.3, 0.3) # Your pre-defined bounds from TOST
)
bf_interval
bf_ratio <- bf_interval[1] / bf_interval[2]
bf_ratio


R_vs_C <- subset(data, treatment %in% c(2, 3))
R_vs_C$treatment <- droplevels(R_vs_C$treatment)
bf_interval <- ttestBF(
  formula = i_vote ~ treatment,
  data = R_vs_C,
  nullInterval = c(-0.3, 0.3) # Your pre-defined bounds from TOST
)
bf_interval
bf_ratio <- bf_interval[1] / bf_interval[2]
bf_ratio

## 3

R_vs_H_3 <- subset(data, treatment %in% c(1, 3)& bid == 3)
R_vs_H_3$treatment <- droplevels(R_vs_H_3$treatment)
bf_interval <- ttestBF(
  formula = i_vote ~ treatment,
  data = R_vs_H_3,
  nullInterval = c(-0.3, 0.3) # Your pre-defined bounds from TOST
)
bf_interval
bf_ratio <- bf_interval[1] / bf_interval[2]
bf_ratio

R_vs_C_3 <- subset(data, treatment %in% c(2, 3)& bid == 3)
R_vs_C_3$treatment <- droplevels(R_vs_C_3$treatment)
bf_interval <- ttestBF(
  formula = i_vote ~ treatment,
  data = R_vs_C_3,
  nullInterval = c(-0.3, 0.3) # Your pre-defined bounds from TOST
)
bf_interval
bf_ratio <- bf_interval[1] / bf_interval[2]
bf_ratio


## 8

R_vs_H_8 <- subset(data, treatment %in% c(1, 3)& bid == 8)
R_vs_H_8$treatment <- droplevels(R_vs_H_8$treatment)
bf_interval <- ttestBF(
  formula = i_vote ~ treatment,
  data = R_vs_H_8,
  nullInterval = c(-0.3, 0.3) # Your pre-defined bounds from TOST
)
bf_interval
bf_ratio <- bf_interval[1] / bf_interval[2]
bf_ratio

R_vs_C_8 <- subset(data, treatment %in% c(2, 3)& bid == 8)
R_vs_C_8$treatment <- droplevels(R_vs_C_8$treatment)
bf_interval <- ttestBF(
  formula = i_vote ~ treatment,
  data = R_vs_C_8,
  nullInterval = c(-0.3, 0.3) # Your pre-defined bounds from TOST
)
bf_interval
bf_ratio <- bf_interval[1] / bf_interval[2]
bf_ratio





```

## Table B5: Treatment effect regression

```{r}
R_vs_H_3 <- subset(data, treatment %in% c(1, 3)&bid == 3)
R_vs_C_3 <- subset(data, treatment %in% c(1, 2)&bid == 3)
data_3 <- subset(data, bid == 3)

model_1 <- glm(i_vote ~hypo+female+year+employed+eco_fin+volunteer, 
               data = R_vs_H_3, 
               family = binomial(link = "logit"))
summary(model_1)
AIC(model_1)
BIC(model_1)
logLik(model_1)
nobs(model_1)


model_2  <- glm(i_vote ~ conq+female+year+employed+eco_fin+volunteer, 
               data = R_vs_C_3, 
               family = binomial(link = "logit"))
summary(model_2)
AIC(model_2)
BIC(model_2)
logLik(model_2)
nobs(model_2)

model_3 <- glm(i_vote ~hypo+conq+female+year+employed+eco_fin+volunteer, 
               data = data_3, 
               family = binomial(link = "logit"))
summary(model_3)
AIC(model_3)
BIC(model_3)
logLik(model_3)
nobs(model_3)

###############

R_vs_H_8 <- subset(data, treatment %in% c(1, 3)&bid == 8)
R_vs_C_8 <- subset(data, treatment %in% c(1, 2)&bid == 8)
data_8 <- subset(data, bid == 8)

model_1 <- glm(i_vote ~hypo+female+year+employed+eco_fin+volunteer, 
               data = R_vs_H_8, 
               family = binomial(link = "logit"))
summary(model_1)
AIC(model_1)
BIC(model_1)
logLik(model_1)
nobs(model_1)

model_2  <- glm(i_vote ~ conq+female+year+employed+eco_fin+volunteer, 
               data = R_vs_C_8, 
               family = binomial(link = "logit"))
summary(model_2)
AIC(model_2)
BIC(model_2)
logLik(model_2)
nobs(model_2)

model_3 <- glm(i_vote ~hypo+conq+female+year+employed+eco_fin+volunteer, 
               data = data_8, 
               family = binomial(link = "logit"))
summary(model_3)
AIC(model_3)
BIC(model_3)
logLik(model_3)
nobs(model_3)


```




## Table B6-: Certainty correction


```{r}
# Run Table 7 first

### 3% Bid
# Original percentages (no correction)
orig_perc <- data3 %>%
  group_by(treatment) %>%
  summarise(orig = mean(i_vote, na.rm = TRUE) * 100, .groups = "drop")
orig_perc

# Compute percentages for Eq.2 (recoding against -> in favor)
eq2_results <- lapply(ci_thresholds, function(Ci) {
  get_percent(data8, "eq2", Ci) %>%
    rename(!!paste0("Ci<=", Ci) := prop)
}) %>% bind_cols()
eq2_results

# Compute percentages for Eq.3 (recoding in favor -> against)
eq3_results <- lapply(ci_thresholds, function(Ci) {
  get_percent(data8, "eq3", Ci) %>%
    rename(!!paste0("Ci<=", Ci) := prop)
}) %>% bind_cols() 
eq3_results

### Full sample
# Original percentages (no correction)
orig_perc <- data %>%
  group_by(treatment) %>%
  summarise(orig = mean(i_vote, na.rm = TRUE) * 100, .groups = "drop")
orig_perc

# Compute percentages for Eq.2 (recoding against -> in favor)
eq2_results <- lapply(ci_thresholds, function(Ci) {
  get_percent(data, "eq2", Ci) %>%
    rename(!!paste0("Ci<=", Ci) := prop)
}) %>% bind_cols()
eq2_results

# Compute percentages for Eq.3 (recoding in favor -> against)
eq3_results <- lapply(ci_thresholds, function(Ci) {
  get_percent(data, "eq3", Ci) %>%
    rename(!!paste0("Ci<=", Ci) := prop)
}) %>% bind_cols() 
eq3_results

```